---
title: "Model fitting"
author: "Chu-Chang Ku"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Model fitting

Under the structure of Bass-SIR model, we provide three models in the family for fitting 

- **Bass-SIR** Bass-SIR model: $\frac{dI}{dt} = (\kappa + \beta I)\frac{m-I-A}{m} - \gamma I$
- **SIR** ordinary SIR model, which fixed $\kappa$ to zero
- **Growth** logistic growth model, which fixed $\beta$ to zero


### Load the package as a starter
```{r}
library(BassSIR)
```


### Input data

We use the data of COVID-19 in Hubei as an example 
```{r, echo = FALSE}
cases <- as_bass_data(n_covid19$Hubei, id = "Hubei")
```


### Fitting and summarising
```{r, results="hide"}
est1 <- BassSIR::fit(cases, r_rec = 1/22.2, r_death = 1/22.3, type = "BassSIR")
est2  <- BassSIR::fit(cases, r_rec = 1/22.2, r_death = 1/22.3, type = "SIR")
est3  <- BassSIR::fit(cases, r_rec = 1/22.2, r_death = 1/22.3, type = "Growth")
```


```{r}
summary(est1)
```


```{r}
summary(est2)
```


```{r}
summary(est3)
```


### Model comparison

- DIC: Deviance Information Criteria, lower is better
- Deviance: narrower is more stable, lower is better
- Bayes factor: higher is better

```{r}
compare_models(BassSIR = est1, SIR = est2, Growth = est3)
```

